---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```

<!-- badges: start -->
<!-- badges: end -->

# Overview

User-friendly and flexible algorithm for time series **segmentation** with a
regression model governed by a hidden Markov process.

Hidden Markov Model Regression (HMMR) for segmentation of time series with 
regime changes. The model assumes that the time series is governed by a 
sequence of hidden discrete regimes/states, where each regime/state has 
Gaussian regressors as observations. The model parameters are estimated by MLE 
via the EM algorithm.

# Installation

You can install the development version of HMMR from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/HMMR_r")
```

To build *vignettes* for examples of usage, type the command below instead:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/HMMR_r", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         build_vignettes = TRUE)
```

Use the following command to display vignettes:

```{r, eval = FALSE}
browseVignettes("HMMR")
```

# Usage

```{r, message = FALSE}
library(HMMR)
```

```{r, echo = TRUE}
# Application to a toy data set
data("toydataset")
x <- toydataset$x
y <- toydataset$y

K <- 5 # Number of regimes (states)
p <- 3 # Dimension of beta (order of the polynomial regressors)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

n_tries <- 1
max_iter <- 1500
threshold <- 1e-6
verbose <- TRUE

hmmr <- emHMMR(X = x, Y = y, K, p, variance_type, n_tries, 
               max_iter, threshold, verbose)

hmmr$summary()

hmmr$plot()
```

```{r, echo = TRUE}
# Application to a real data set
data("realdataset")
x <- realdataset$x
y <- realdataset$y2

K <- 5 # Number of regimes (states)
p <- 3 # Dimension of beta (order of the polynomial regressors)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

n_tries <- 1
max_iter <- 1500
threshold <- 1e-6
verbose <- TRUE

hmmr <- emHMMR(X = x, Y = y, K, p, variance_type, 
               n_tries, max_iter, threshold, verbose)

hmmr$summary()

hmmr$plot()
```

# Model selection

In this package, it is possible to select models based on information criteria 
such as **BIC**, **AIC** and **ICL**.

The selection can be done for the two following parameters:

 * **K**: The number of regimes;
 * **p**: The order of the polynomial regression.

Let's select a HMMR model for the following time series **Y**:

```{r, message = FALSE}
data("toydataset")
x <- toydataset$x
y <- toydataset$y

plot(x, y, type = "l", xlab = "x", ylab = "Y")
```

```{r, message = FALSE}
selectedhmmr <- selectHMMR(X = x, Y = y, Kmin = 2, Kmax = 6, pmin = 0, pmax = 3)

selectedhmmr$plot(what = "smoothed")
```
